### 2016-07-28 main.tex
Nothing much.  Interim checkin.

We begin with a few hundred recordings of a given bird's song.  Male
zebra finch song is most highly stereotyped when a female is present
(``directed song'') and slightly more variable otherwise
(``undirected''); we train and test on undirected song since this is
more challenging.  The songs are recorded inside a sound-isolating
chamber in which was mounted a recording microphone (Audio-Technica
AT803).  The songs are time-aligned as described in \cite{Poole2012}.

>>>>

We begin with a few hundred recordings of a given bird's song, as well as calls, cage noise, and other non-song audio data.  Male
zebra finch song is most highly stereotyped when a female is present
(``directed song'') and slightly more variable otherwise
(``undirected''); we train and test on undirected song since this is
more challenging.  Recordings were made inside a sound-isolating
chamber in which was mounted a recording microphone (Audio-Technica
AT803).  The songs were time-aligned as described in \cite{Poole2012}.
